{\small
\noindent
\textbf{Recurring awards and funds}

\smallskip
\noindent
These brief descriptions summarize the recurring named department awards,
scholarships, fellowships, and endowments that appear throughout the student
entries. Links point to department award pages or newsletters; where the
department does not publish a one-line formal definition, the summary follows
the award name and how the fund is grouped on department materials. One-off
external honors, society inductions, and presentation placements are left to
the student entries themselves.

\medskip
\noindent
\textbf{Scholarships, fellowships, and endowments}

\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Armstrong Physics Endowment}{Endowed department support fund established by alumni Barbara and Scott Armstrong for student support in physics.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{B.\,H.\ Rose Endowment Fund}{Endowed department fund that supports graduate student funding in physics.}
\awarddescription{https://physics.missouri.edu/sites/default/files/file-uploads/2021-03/dpanewsletterfall2020-optimized_0.pdf}{Carl \& Brynn Anderson Graduate Student Award Fund in Physics}{Graduate-student support fund used in department materials for physics travel support.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Clifford W.\ Tompson Scholarship in Physics}{Recurring scholarship supporting physics students in the department.}
\awarddescription{https://physics.missouri.edu/department-newsletters}{Donald L.\ and Lona Lewis Packwood Endowed Undergraduate Scholarship Fund in Physics}{Recurring undergraduate scholarship fund established through alumni support for physics students.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Eli Stuart Haynes \& Nola Anderson Haynes Scholarship}{Recurring department scholarship fund supporting student work in physics and astronomy.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Ernest W.\ Landen Fellowship in Physics}{Recurring fellowship support for students in physics.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Eugene B.\ Hensley Scholarship in Physics}{Recurring scholarship awarded within the department's physics student support funds.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Guy Schupp Scholarship Fund}{Recurring scholarship fund supporting students in the department.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{James L.\ and Dora D.\ Fergason Fund for Excellence in Physics}{Department fund recognizing and supporting excellence in physics.}
\awarddescription{https://physics.missouri.edu/department-newsletters}{John H.\ Letcher Graduate Student Scholarship}{Graduate-student scholarship first awarded in the 2025 department newsletter cycle.}
\awarddescription{https://physics.missouri.edu/department-newsletters}{Melvin Y.\ Mora Undergraduate Scholarship Fund}{Recurring undergraduate scholarship fund honoring Melvin Y.\ Mora.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Newell S.\ Gingrich Physics Scholarship Fund}{Recurring scholarship fund for physics students.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Newell S.\ Gingrich Physics \& Astronomy Endowment}{Endowed student-support fund spanning both physics and astronomy.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{O.\,M.\ Stewart Scholarship}{Recurring department scholarship for physics and astronomy students.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Paul E.\ Basye Undergraduate Scholarship}{Recurring undergraduate scholarship supporting physics students.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Rose Marie Dishman Endowed Scholarship in Physics}{Endowed scholarship supporting students in physics.}
\awarddescription{https://physics.missouri.edu/department-newsletters}{Samuel S.\ Laws Scholarship}{Recurring scholarship fund supporting physics and astronomy students.}

\medskip
\noindent
\textbf{Department awards}

\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Carl \& Brynn Anderson Travel Award}{Department graduate travel award supporting research or conference travel.}
\awarddescription{https://physics.missouri.edu/department-newsletters}{Dorina Kosztin Memorial Award}{Department memorial award recognizing student excellence and service.}
\awarddescription{https://physics.missouri.edu/department-newsletters}{Gerald Fishman Travel Award}{Named travel-support award that appears in the earlier department newsletters for student travel.}
\awarddescription{https://physics.missouri.edu/news/celebrating-student-awards-scholarships-and-recognition}{Harry E.\ Hammond Teaching Assistant Award}{Department award recognizing strong teaching-assistant performance.}
\awarddescription{https://physics.missouri.edu/news/physics-leaders-meeting}{Ron Boain \& Catherine Rangel-Boain Dissertation Award}{Annual department prize for the best doctoral dissertation.}
\awarddescription{https://physics.missouri.edu/news/physics-leaders-meeting}{Ron Boain \& Catherine Rangel-Boain Travel Award}{Graduate travel award funded to help students attend professional conferences and research trips.}
}
